Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-25 Paper.tex
Change hypertarget captions to empty strings

\begin{itemize}
\item $I_a$, the address of the account which owns the code that is executing.
\item $I_o$, the sender address of the transaction that originated this execution.
\item $I_p$, the price of gas in the transaction that originated this execution.
\item $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.
\item $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.
\item $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.
\item $I_\mathbf{b}$, the byte array that is the machine code to be executed.
\item $I_H$, the block header of the present block.
\item $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).
\item $I_w$, the permission to make modifications to the state.
\end{itemize}

>>>>

\begin{itemize}\hypertarget{address_of_account_which_owns_code_I__a_def_words}{}
\item $I_a$, the address of the account which owns the code that is executing.\hypertarget{address_of_sender_of_tx_that_originated_execution_I__o}{}
\item $I_o$, the sender address of the transaction that originated this execution.\hypertarget{gas_price_in_tx_that_originated_execution_I__p}{}
\item $I_p$, the price of gas in the transaction that originated this execution.\hypertarget{execution_input_data_I__d}{}
\item $I_\mathbf{d}$, the byte array that is the input data to this execution; if the execution agent is a transaction, this would be the transaction data.\hypertarget{the_address_of_the_account_which_caused_the_code_to_be_executing_I__s}{}
\item $I_s$, the address of the account which caused the code to be executing; if the execution agent is a transaction, this would be the transaction sender.\hypertarget{Wei_value_exec}{}
\item $I_v$, the value, in Wei, passed to this account as part of the same procedure as execution; if the execution agent is a transaction, this would be the transaction value.\hypertarget{exec_machine_code_I__b}{}
\item $I_\mathbf{b}$, the byte array that is the machine code to be executed.\hypertarget{exec_block_header_I__H}{}
\item $I_H$, the block header of the present block.\hypertarget{exec_call_or_create_depth_I__e}{exec_call_or_create_depth_I__e}
\item $I_e$, the depth of the present message-call or contract-creation (i.e. the number of {\small CALL}s or {\small CREATE}s being executed at present).\hypertarget{exec_permission_to_modify_state_I__w}{}
\item $I_w$, the permission to make modifications to the state.
\end{itemize}
